---
title: "Looking at bee colony losses"
author: "Alex Dang"
date: "3/3/2022"
output: 
  html_document:
    downcute_theme: "chaos"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.path = '../output/')
```

## Load libraries 
Loading all the necessary R packages for plotting data

```{r}
library(kableExtra)
library(tidyverse)
library(here)
library(sysfonts)
library(showtextdb)
library(showtext)
library(beyonce)
```

## Adding fonts
Adding fonts for plot by retrieving them from GoogleFonts browser

```{r}
font_add_google("Yanone Kaffeesatz", "yanone")
```

## Load data
Pulling bee colony data frame

```{r}
BeeColony<-read_csv(here("week_6", "data", "colony.csv"))
view(BeeColony)
```

## Data analysis
### Data table
First, set up data table with desired variables and values for plotting

Data table to represent the bee colony losses in the 10 most populated states in America:
```{r}
most_pop<-BeeColony %>% 
  drop_na() %>% 
  filter(state == "California"| state == "Texas"| state == "Florida"| state == "New York"| state == "Pennsylvania"| 
           state == "Illinois"| state == "Ohio"| state == "Georgia"| state == "North Carolina"| state == "Michigan") %>% 
  select("year", "months", "state", "colony_max", "colony_lost")

view(most_pop)

most_pop %>% 
  kbl() %>% 
  kable_material() %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), 
                full_width = FALSE, fixed_thead = T, position = "center", 
                font_size = 12)
```

### Data plotting
Now, plot the data
```{r bees1, fig.width=8, fig.height=4, fig.asp=1.2, fig.align='center', fig.cap="Bee Colony plot"}
showtext_auto() 
most_pop %>% 
  ggplot(aes(x = colony_max, y = colony_lost, color = state)) +
  geom_point() +
  labs(title = "Bee Colony Losses in the 10 Most Populated States of America",
       x = "Max Colonies", y = "Colonies Lost",
       caption = "Bee Colony Losses Data from USDA") +
  theme(plot.title = element_text(size = 26, hjust = 0.5, family = "yanone"),
        axis.title = element_text(size = 14),
        panel.background = element_rect(fill = "beige"),
        panel.border = element_rect(fill = NA, color = "black"), 
        legend.key = element_rect(fill = "beige"),
        legend.title = element_text(size = 16))
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
