---
title: "Bad/Good Plots"
author: "Alex Dang"
date: "3/14/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.path = '../output/')
```

## Abstract
Two plots are created using the same "Chocolate Bar Ratings" data set from Tidy Tuesday Repository. One plot represents a 'Bad plot', where it is incomprehensive and fail to represent its data set. The second plot represents a 'Good plot' that demonstrate the data set clearly and is easy to understand.


## Load libraries
Loading all the necessary libraries
```{r}
library(tidyverse)
library(here)
library(sysfonts)
library(showtextdb)
library(showtext)
library(emojifont)
library(beyonce)

## Add font
font_add_google("Yanone Kaffeesatz", "yanone")
```


## Load data frame
[Chocolate data frame](https://github.com/Biol551-CSUN/Dang/blob/main/week_7/data/chocolate.csv)
```{r}
Chocolate<-read_csv(here("week_7", "data", "chocolate.csv"))
view(Chocolate)
```


## Bad plot data analysis
This section will illustrate the construction of a 'Bad plot'.

What makes this a bad plot?

1. It is too compacted. Too much going on. Some data wrangling is needed to a cleaner data frame and plot.

2. Background color is not suitable. It is difficult to see the plot and the color does not appear "brown". A different color palette would be a better approach.

3. Plot title does not clearly explains what the plot is of. 

4. Title sizes are too small compared to the entire plot.
```{r}
ggplot() +
  geom_boxplot(data = Chocolate, 
               aes(x = rating, y = country_of_bean_origin,
                   color = cocoa_percent)) +
  labs(title = "Chocolate!!!",
       x = "Rating", y = "Country of Origin",
       caption = "Flavors of Cacao by Will Canniford on Goldberg",
       color = "Cocoa %") +
  theme(panel.background = element_rect(fill = "brown2"))
```


## Good plot data analysis
This section will illustrate the construction of a 'Good plot'.
```{r}
Chocolate_clean<-Chocolate %>% 
  drop_na() %>%  
  select(country_of_bean_origin, cocoa_percent, rating) %>% 
  filter(country_of_bean_origin == "Ghana"| country_of_bean_origin == "Indonesia"| country_of_bean_origin == "Nigeria"| 
           country_of_bean_origin == "Cameron"| country_of_bean_origin == "Ivory Coast"| country_of_bean_origin == "Brazil"|
           country_of_bean_origin == "Ecuador"| country_of_bean_origin == "Peru"| country_of_bean_origin == "Colombia"| 
           country_of_bean_origin == "Dominican Republic")
  
  
view(Chocolate_clean)

showtext_auto()

ggplot(data = Chocolate_clean, 
             mapping = aes(x = rating, y = cocoa_percent, color = country_of_bean_origin)) +
  geom_point() +
  labs(title = "Chocolate Rating Relative to Cocoa Percent in Most Cocoa Producing Countries", 
       x = "Rating", y = "Cocoa %", color = "Country of Origin", 
       caption = "Flavors of Cacao by Will Canniford on Goldberg") + 
  scale_color_manual(values = beyonce_palette(81)) +
  theme(plot.title = element_text(size = 34, hjust = 0.5, family = "yanone"),
        axis.title = element_text(size = 26, family = "yanone"),
        panel.border = element_rect(fill = NA, color = "black"), 
        panel.background = element_rect(fill = "lavenderblush"), 
        legend.title = element_text(size = 26, family = "yanone"))
```